\chapter{Where Quantum Physics Slots In}

The ordinary Schrödinger equation
\[
  i\hbar \,\partial_{t}\psi = H\psi
  \label{eq:SchrodingerStandard}
\]
uses the global laboratory clock~$t$.  
Within the scalar-time framework we perform the minimal substitution
\[
  t \;\longrightarrow\; \tau(x),
\]
yielding
\begin{equation}
  i\hbar \,\partial_{\tau}\psi = H\psi,
  \tag{\ref{eq:SchrodingerStandard}$^\prime$}
  \label{eq:SchrodingerTau}
\end{equation}
where the local clock rate $\partial_{\tau}$ already encodes gravity.

\input{figs/fig12_C5_Wave_Packet} 

\paragraph{Wave-packet test.}
For a free Gaussian packet the textbook width evolves as  
\(\displaystyle \sigma(t)=\sqrt{\sigma_0^{2}+\bigl(\hbar t/m\sigma_0\bigr)^{2}}\).
Starting with $\sigma_0=0.1\,\mathrm{nm}$ an electron spreads to
\((\sigma\!\approx\!115\,\text{\AA}\) after $10\,\mathrm{fs}$ under normal time
(orange curve).  
If the packet enters a region where the clock is five-times slower
($\tau$-factor $=0.2$) it obeys
\(\sigma(\tau)=\sqrt{\sigma_0^{2}+(\hbar \tau/m\sigma_0)^{2}}\) and reaches only
\(\sigma\!\approx\!22\,\text{\AA}\) (red curve).  
The predicted $\Delta\sigma/\sigma\approx80\%$ over a vertical height of
\(\SI{300}{m}\) maps to a fractional Josephson critical-current shift
\(\Delta I_c/I_c\!\simeq\!4\times10^{-15}\), within reach of state-of-the-art
SQUIDs.

\paragraph{Hawking-radiation note.}
Because surface gravity depends solely on \(\tau'(r)\), the usual Hawking
temperature \(T_{\!H}= \hbar c^{3}\!/\bigl(8\pi GM k_B\bigr)\) is recovered
unchanged.

\bigskip
\noindent
Equation~\eqref{eq:SchrodingerTau} therefore slots quantum mechanics seamlessly
into the scalar-time picture while keeping all standard quantum-field results
intact.
